The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-03-16 paper/paper.tex
FFNN fixes

The method is a Feed Forward Neural Network (FFNN), a classic type of neural network.
This implementation used the Keras API in the TensorFlow library. Three components, a flattener, and two 
dense layers of ReLu neurons, were optimized by ADAM on the sparse categorical cross-entropy of the classifications.
A MinMaxScaler was used to pre-process the data, and the training stopped when there was no improvement in the  
validation loss for three consecutive epochs, to avoid overfitting.

>>>>

The method is a Feed Forward Neural Network (FFNN), a classic type of neural network.
This implementation used the Keras API in the TensorFlow library. Three components, a flattener, and two 
dense layers of ReLu neurons, were optimized by ADAM on the sparse categorical cross-entropy of the classifications.
A StandardScaler was used to pre-process the data, and the training stopped when there was no improvement in the  
validation loss for three consecutive epochs, to avoid overfitting.

The network is trained using the galaxies' magnitudes, colours and band-triplets as well as their errors to assign them to 
the redshift bins.
Prior to processing the training and validation data, the non-detection placeholder magnitudes (30.0) were replaced with 
an approximation of the $1\sigma$ detection limit as an estimate for the sky noise threshold, where Signal to Noise ratio, 
S/N, equals 1. We first compute the error equivalent of $dm = 2.5 \log(1 + N/S)$ where $dm \sim 0.7526$ 
magnitudes for $N/S = 1$, and then fit a logarithmic model to the magnitude as a function of its error 
for different bands in the training data. This gives us the magnitude corresponding to this limit 
and in order to be consistent we use this value along with its error to replace the non-detections 
everywhere during the process.
